High-Dimensional Regularized Discriminant Analysis

### 2013-12-30 reports/paper-hdrda.Rnw
Abstract polish recommended by Caleb.

\citeauthor{Friedman:1989tm} proposed the popular regularized discriminant
analysis (RDA) classifier that utilizes a biased covariance-matrix estimator
that partially pools the sample covariance matrices from linear and quadratic
disriminant analysis before shrinking the resulting estimator towards a scaled
identity matrix. The RDA classifier's two tuning parameters are typically
estimated via a computationally burdensome cross-validation procedure from a
grid of candidate values. We reformulate the RDA classifier in the
high-dimensional setting and then show that the classification decision rule is
equivalent to one in a subspace having a much lower dimension. As a result, the
dimension reduction involved yields a substantial reduction in computation
during model selection. Our parameterization also offers interpretability
previously lacking with the RDA classifier. We demonstrate with three artificial
and four real high-dimensional data sets that our proposed classifier is often
superior to several recently proposed sparse and regularized classifiers in
terms of classification accuracy. Finally, we provide an implementation of our
proposed classifier in the {\tt sparsediscrim} R package, available on CRAN.

>>>>

\citeauthor{Friedman:1989tm} proposed the popular regularized discriminant
analysis (RDA) classifier that utilizes a biased covariance-matrix estimator to
partially pool the sample covariance matrices from linear and quadratic
disriminant analysis before shrinking the resulting estimator towards a scaled
identity matrix. The RDA classifier's two tuning parameters are typically
estimated via a computationally burdensome cross-validation procedure from a
grid of candidate values. We reformulate the RDA classifier in the
high-dimensional setting and then show that the classification decision rule is
equivalent to one in a subspace having a much lower dimension. As a result, the
dimension reduction involved yields a substantial reduction in computation
during model selection. Our parameterization also offers interpretability
previously lacking with the RDA classifier. We demonstrate with three artificial
and four real high-dimensional data sets that our proposed classifier is often
superior to several recently proposed sparse and regularized classifiers in
terms of classification accuracy. Finally, we provide an implementation of our
proposed classifier in the {\tt sparsediscrim} R package, available on CRAN.
